\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-04-26 chapters/1_intro.tex
Rewrite contr. graph formalism and update exp sec.

\emph{Instance segmentation} is a task of computer vision consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
The most success in instance segmentation (IS) has been achieved by applying deep learning \cite{he2017mask,romera2016recurrent,liu2018affinity}. There are two main types of successful deep learning approaches to IS: proposal-based and proposal-free methods. Proposal-based methods consist of two steps: object detection, for example by finding bounding boxes, and assigning pixels to the detected objects \cite{he2017mask,dai2016instance,li2017fully}. Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example microscopy images of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes. 
% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
Proposal-free methods perform IS by directly predicting pixel features and then using a clustering algorithm for grouping pixels into object instances \TODO{REFS}. In this work, we focus on a proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance. Recently, \cite{liu2018affinity} used this approach and achieved performances comparable to proposal-based methods on the Cityscapes dataset; \UPDATE{similarly, the method was used in \cite{wolf2018mutex} to achieve state-of-the-art results in a neuron segmentation challenge.}

>>>>

\emph{Instance segmentation} is a task of computer vision consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
The most success in instance segmentation (IS) has been achieved by applying deep learning \cite{he2017mask,romera2016recurrent,liu2018affinity}. There are two main types of successful deep learning approaches to IS: proposal-based and proposal-free methods. Proposal-based methods consist of two steps: object detection, for example by finding bounding boxes, and assigning pixels to the detected objects \cite{he2017mask,dai2016instance,li2017fully}. Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes. 
% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
Proposal-free methods perform IS by directly predicting pixel features and then using a clustering algorithm for grouping pixels into object instances \TODO{REFS}. In this work, we focus on a proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance. Recently, \cite{liu2018affinity} used this approach and achieved performances comparable to proposal-based methods on the Cityscapes dataset; \UPDATE{similarly, the method was used in \cite{wolf2018mutex} to achieve state-of-the-art results in a neuron segmentation challenge.}

### 2019-04-26 chapters/3_algorithm.tex
Rewrite contr. graph formalism and update exp sec.

Given a simple graph $\mathcal{G}(V,E)$, we call the set $\Pi$ a \emph{clustering} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for every $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$.

In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ to each edge $e \in E$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining positively weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph. In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters. 
Often, graphs with both attractive and repulsive edge attributes are described in terms of a \emph{signed} cost function $\cost: E \rightarrow \mathbb{R}$ that combines both edge weights into one signed scalar number: 
\begin{equation}
\cost_e = w_e^+ - w_e^- \in \mathbb{R}, \quad \quad \forall e \in E
\end{equation}
Graphs that have only positive weights can be clearly seen as special cases of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ and $c_e \geq 0$ for every $e \in E$.

\paragraph{Linkage criterion}\label{par:linkage_criterion_def} We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge $e_{uv}\in E$ in the original graph connecting a node $u\in S_1$ to a node $v\in S_2$:
\begin{equation}
 \text{$S_1, S_2 \in \Pi$ are \emph{adjacent}} \quad \Longleftrightarrow  \quad  \mathcal{B}(S_1,S_2) \equiv \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \} \neq \emptyset
\end{equation}
where we defined the set of edges connecting two adjacent clusters as \UPDATE{\emph{boundary}} \UPDATE{$\mathcal{B}(S_1,S_2)$}. The interaction between two clusters $S_1, S_2$ is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges in the boundary $\mathcal{B}(S_1,S_2)$. In hierarchical agglomerative clustering and graphs with only positive weights, some examples of linkage criterion statistics are \emph{maximum} (single-linkage clustering), \emph{minimum} (complete-linkage clustering) and arithmetical average (average-linkage clustering).

\paragraph{Multicut and correlation clustering} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:
\begin{equation}
E_\Pi^0 \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^1_\Pi \equiv E \setminus E^0_\Pi.
\end{equation}
% \begin{align}
% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
% E^1_\Pi &= E \setminus E^0_\Pi.
% \end{align}
The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ associated to the clustering $\Pi$. The instance of the NP-hard \emph{weighted correlation clustering} or \emph{minimum cost multicut problem} w.r.t. $\mathcal{G}(V,E,w^+, w^-)$ \cite{kappes2011globally,chopra1991multiway,andres2015lifting} is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following optimization problem/binary integer program:
\begin{equation}
% \min_\Pi \texttt{MC}(\Pi) \equiv
 \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
 \begin{cases} 
 1 & \text{if } e\in E^1_\Pi \\
 0 & \text{otherwise}.
 \end{cases}
\end{equation}
In the next chapters we will use this objective as a way to measure how balanced is a clustering found by the tested agglomerative clustering algorithms.

@@

Given a graph $\mathcal{G}(V,E,w^+, w^-)$, the proposed generalized clustering uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters. Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b} and \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c}).

@@

\paragraph{Edge contraction and update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
An efficient way of implementing these updates can be achieved by representing the clustering $\Pi$ with a \emph{contracted graph} $\mathcal{G'}(\mathcal{G}, \Pi)$, such that each of its nodes is associated to a cluster $S \in \Pi$, edges represent adjacency-relationships between clusters and edge weights inter-cluster interactions.
\UPDATE{Every time a pair of neighboring clusters is merged, the contracted graph is updated by performing an edge contraction and merging two nodes. After the edge contraction, the only cluster interactions that need to be updated are those between nodes connected by double edges in the contracted graph (see Fig. \ref{fig:edge_contraction_and_contr_graph}, step b). For simple linkage criteria, these updates can be easily computed with an update rule $f$ that depends only on the interactions at the previous step }
% As a result, the merged node could be linked to some of its neighbors by double edges . , representing the fact that their interaction should be updated. This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges. 
\TODO{such a mess...}
\UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}

>>>>

Given a simple graph $\mathcal{G}(V,E)$, we call the set $\Pi$ a \emph{clustering} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for every $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. In the following we denote the cluster associated with node $u$ as $S_u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}

In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ to each edge $e \in E$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining positively weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph. In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters. 
Often, graphs $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes are also defined as $\mathcal{G}(V,E,\cost)$, where $\cost: E \rightarrow \mathbb{R}$ represents a \emph{signed interaction} that combines both attraction and repulsion into one signed scalar number: % space: make equation in line
\begin{equation}
\cost_e = w_e^+ - w_e^- \in \mathbb{R}, \quad \quad \forall e \in E
\end{equation}
Graphs that have only positive weights can be clearly seen as a special case of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ and $c_e \geq 0$ for every $e \in E$.

\paragraph{Inter-cluster interaction}\label{par:linkage_criterion_def} We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_1$ to a node $v\in S_2$. In agglomerative HC, the interaction $\interact_{S_1,S_2}$ between two clusters $S_1, S_2$ is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges connecting clusters $S_1$ and $S_2$. For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
\begin{equation}\label{eq:max_linkage}
\mathscr{W}_{S_1,S_2} = \max_{e\in U} \cost(e), \qquad \text{where}\quad U = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
\end{equation}
Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.
% \begin{equation}
%  \text{$S_1, S_2 \in \Pi$ are \emph{adjacent}} \quad \Longleftrightarrow  \quad  \mathcal{B}(S_1,S_2) \equiv \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \} \neq \emptyset
% \end{equation}
% where we defined the set of edges connecting two adjacent clusters as \UPDATE{\emph{boundary}} \UPDATE{$\mathscr{W}(S_1,S_2) , \mathcal{G}'_{\mathcal{G},\Pi}(V',E')$}.  in the boundary $\mathcal{B}(S_1,S_2)$. Some examples of linkage criterion statistics are \emph{maximum} (single-linkage), \emph{minimum} (complete-linkage) and average (average-linkage).

\paragraph{Multicut and correlation clustering} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:
\begin{equation}
E_\Pi^0 \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^1_\Pi \equiv E \setminus E^0_\Pi.
\end{equation}
% \begin{align}
% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
% E^1_\Pi &= E \setminus E^0_\Pi.
% \end{align}
The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ associated to the clustering $\Pi$. The instance of the NP-hard \emph{weighted correlation clustering} or \emph{minimum cost multicut problem} w.r.t. $\mathcal{G}(V,E,w^+, w^-)$ \cite{kappes2011globally,chopra1991multiway,andres2015lifting} is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following optimization problem/binary integer program:
\begin{equation}
% \min_\Pi \texttt{MC}(\Pi) \equiv
 \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
 \begin{cases} 
 1 & \text{if } e\in E^1_\Pi \\
 0 & \text{otherwise}.
 \end{cases}
\end{equation}
In the next chapters we will use this objective as a way to measure how much a clustering is balanced.

@@

The proposed generalized clustering uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters. Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b} and \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c}).

@@

\paragraph{Edge contraction and update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph. Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$, edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights are given by inter-cluster interactions, i.e. $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
For the linkage criteria tested in this work, when clusters $S_u,S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can easily express them in terms of a simple \emph{update rule} $f$. For instance, in the case of the single-linkage criterion defined in Eq. \ref{eq:max_linkage}, we can use the following simple max-update-rule to recompute the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$:
\begin{equation}
  \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
\end{equation}

\UPDATE{Every time a pair of clusters is merged, the contracted graph is updated by performing an edge contraction and merging the associated nodes. The only interactions that then need to be updated are those between nodes that after the edge contraction happen to be connected by double edges (see Fig. \ref{fig:edge_contraction_and_contr_graph}, step b). For basic linkage criteria, e.g. \emph{max} or \emph{min}, the new interaction can be formulated in terms of an \emph{update rule} $f$ depending only on the these updates can be computed with an update rule $f$ that depends only on the interactions at the previous step }
% As a result, the merged node could be linked to some of its neighbors by double edges . , representing the fact that their interaction should be updated. This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges. 
\TODO{such a mess...} ...without the need of running a loop over the edges of the original graph.
\UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}

### 2019-04-26 chapters/5_experiments_cityscapes.tex
Restructure introduction
Rewrite contr. graph formalism and update exp sec.

% !TEX root = ../agglo_clust_review.tex
\subsection{Results on Cityscapes}
In the experiments on the cityscapes dataset, we used the pipeline proposed by \cite{liu2018affinity} \UPDATE{that currently represents the method not using any external dataset like MS-COCO}...

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on Cityscapes}
A successful proposal-free method was recently presented in \cite{liu2018affinity} and a setup equivalent to the one described in Sec. \ref{sec:grid_graph} but uses a more complex pipeline to select region of interests in the image, predict semantic pixel information that is used to improve pixel affinities, etc... We used exactly their code and pipeline, but we replaced their final agglomeration clustering step with the algorithms proposed in this paper...

In the experiments on the cityscapes dataset, we used the pipeline proposed by \cite{liu2018affinity} \UPDATE{that currently represents the method not using any external dataset like MS-COCO}...

I should mention the main trick in the loss: ignore background pixels (so focus on boundaries!)

### 2019-04-26 chapters/5_experiments_intro.tex
Rewrite contr. graph formalism and update exp sec.

% !TEX root = ../agglo_clust_review.tex

\subsection{Experimental setup and tested datasets}
\begin{itemize}
    \item Define long-range grid graph. (Mention the fact of enforcing local merge)
\item Introduce "Poisson" random graph with a given probability of long-range connections
\item Comment about the short- and long-range distinction in the MWS paper? It does not work that well in practice (applying post-processing to remove small segments is easier and better solution).
\item Ad of course we can think about a classifier that separately predict attraction and repulsion
\item Define offset patterns (link to supplementary material), trained networks (loss, etc...) and setups on cremi and cityscapes 
\item Mention postprocessing step: get rid of tiny segments; on CREMI we use watershed to fill the deleted parts 
\end{itemize}

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on neuron segmentation}

We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes. This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems. While a lot of progress is being made, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}.
\TODO{subsections description}

\subsection{Experimental setup and pixel grid-graph} \label{sec:grid_graph}
\begin{itemize}
\item Define predictions of the classifier (pseudo probabilities) for edge weights
\item Define possible mappings to signed costs
\item Make comment about which version defines nested segmentations and which does not give hirarchical solutions

\end{itemize}

\begin{itemize}
    \item Define long-range grid graph. (Mention the fact of enforcing local merge)
\item Introduce "Poisson" random graph with a given probability of long-range connections
\item Comment about the short- and long-range distinction in the MWS paper? It does not work that well in practice (applying post-processing to remove small segments is easier and better solution).
\item Ad of course we can think about a classifier that separately predict attraction and repulsion
\item Define offset patterns (link to supplementary material), trained networks (loss, etc...) and setups on cremi and cityscapes 
\item Mention postprocessing step: get rid of tiny segments; on CREMI we use watershed to fill the deleted parts 
\end{itemize}
